### 2022-06-10 paper.tex

Sequencing-based assays with single-cell resolution have offered new means to understand the differences between the cells making up a sample. Single-cell RNA sequencing (scRNA-seq) techniques have matured at great pace in recent years. Now, methods to study chromatin are rapidly catching up. Of special interest here is DNA methylation, i.e., the methylation of bases in the DNA, because DNA methylation patterns are passed on to daughter cells in cell division. Especially in mammals, such methylation chiefly occurs at cytosine bases that are immediately after followed by guanine bases, so-called CpG sites.

@@

The standard approach to analyse scBS data is based on methodology developed for the analysis of single-cell RNA-Seq data. Therefore, we will start by briefly reviewing how single-cell \emph{RNA}-Seq data is commonly analyzed, before we discuss scBS data analysis.

>>>>

Sequencing-based assays with single-cell resolution have offered new means to understand the differences between the cells making up a sample. Single-cell RNA sequencing (scRNA-seq) techniques have matured at great pace in recent years. Now, methods to study epigenetics at single-cell resolution are rapidly catching up. Of special interest here is DNA methylation, i.e., the methylation of bases in the DNA, which is passed on to daughter cells in cell division. Especially in mammals, such methylation chiefly occurs at cytosine bases that are immediately after followed by guanine bases, so-called CpG \mbox{(5'--C--phosphate--G--3')} sites.

@@

The standard approach to analyse scBS data is based on methodology developed for the analysis of single-cell RNA-Seq data. Therefore, we will start by briefly reviewing how single-cell \emph{RNA}-Seq data is commonly analysed, before we discuss scBS data analysis.
